Including EW and mixed QCD-EW corrections into PDF fits

### 2020-04-01 paper/sec-introduction.tex
Fixed missing cross ref

The paper is organised as follows. In Sect.~\ref{sec:pineappl} we introduce
{\sc PineAPPL}, we describe its features, we illustrate its operation, and we
assess its performance. In Sect.~\ref{sec:results}, by means of 
{\sc mg5\_AMC@NLO} and {\sc PineAPPL}, we compute fast interpolation grids for 
a representative set of data that is typically included in a fit of PDFs.
In Sect.~\ref{sec:double-counting} we use these results to formulate more 
comprehensively the second problem sketched above, the solution of which, 
however, remains beyond the scope of the current work. We provide an outlook in
Sect~\ref{sec:conclusion}.

>>>>

The paper is organised as follows. In Sect.~\ref{sec:pineappl} we introduce
{\sc PineAPPL}, we describe its features, we illustrate its operation, and we
assess its performance. In Sect.~\ref{sec:results}, by means of 
{\sc mg5\_AMC@NLO} and {\sc PineAPPL}, we compute fast interpolation grids for 
a representative set of data that is typically included in a fit of PDFs.
In Sect.~\ref{sec:doublecounting} we use these results to formulate more 
comprehensively the second problem sketched above, the solution of which, 
however, remains beyond the scope of the current work. We provide an outlook in
Sect~\ref{sec:conclusion}.
